\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-09-21 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

\begin{document}

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs} \\
Answer to Referee 1}

\author{Guillaume \textsc{Daudin}\thanks{%
Université Paris-Dauphine, PSL University, CNRS, 8007, IRD, 260, LEDa, DIAL, 75016, Paris, France ; email: \url{guillaume.daudin@dauphine.psl.eu}}  \qquad J\'{e}r\^{o}me \textsc{H\'{e}ricourt} \thanks{Universit\'{e} de Lille - LEM-CNRS UMR 9221, France \& CEPII, France; email: \url{jerome.hericourt@univ-lille.fr}}\qquad Lise \textsc{Patureau}\thanks{Corresponding author.
University Paris-Dauphine \& PSL University, LEDa, 75016 Paris, France;  email: \url{lise.patureau@dauphine.psl.eu} } }

\date{September 2021}
 \maketitle
\bigskip

We would like to thank you for your insightful comments. They led us to introduce some
significant changes to the paper that we hope address your concerns. We first give you an overview
of the revision (Section\ref{sec:main_changes}) before answering in detail each of your comments (Section\ref{sec:detailed_answers}). Number of sections, pages and equations mentioned in the text refer to the revised version.

@@

\section{Main changes \label{sec:main_changes}}

\begin{itemize}
%\item Based on your comment 1.2 (\textit{The aggregation problem}), we have investigated the case with $s=3$ and $k=10$ for the industry/product aggregation levels respectively. Our initial choice of retaining $s=3$ at the sectoral level, $k=5$ at the product level was driven by the use of Hummel's dataset available over 1974-2004 with $k=5$ the finest degree of aggregation. In the submitted version, we used the original Hummel's database (available on his webpage from 1974 to 2003, which we completed by the US Bureau of census import database over the period 2005-2013. In Hummels' (2007) database, which we use until 2004, the finest degree of classification is at the 5-degree level until 2004. For comparability reasons over time, we have adopted the same degree of classification $k=5$ for the following years (based on the original Census dataset). As a result, in the submitted version, transport costs are estimated at the 3-digit sector level as benchmark estimate, exploiting product heterogeneity at the 5-digit level (for a given origin country, and conditional on year and transport mode).
%
%    Switching to $k=10$ as benchmark disaggregation level for the product dimension would require resorting on US Census dataset only. It is true that the original annual Census data reports trade at the origin country-HS 10 product-district level of aggregation. However, the Census bureau can provide data disaggregated at the $k=10$ product level only starting in 1989. Some of these data are in physical storage and were not accessible because of the Covid-19 pandemic (1989-1996, but also 2000 and 2001). In september 2021, they are still not accessible. Waiting for them contributed to making this revision quite late. This deprives us from the very first years 1974-1996 and 2000-2001. For this period, we can only resort on Hummel's dataset, with $k=5$ the finest product level category. This is a non-negligible cost as we are interested in the long-term evolution of trade costs.
%
%    As a result, we decided to adopt the following strategy in the revised version. As benchmark, we still consider the 5/3 product/sector classification (as in the submitted version), as this allows us to preserve (as far as possible) the largest time coverage. We check the robustness of our results to the 10/3 classification, for the available years. This is made in Section XXX.
%
%    \textbf{LP: Pas sure que ce point doive etre mis ici, pas main change du coup}

@@

\item Based on your comment 1.1 (\textit{The endogeneity problem}), the benchmark regression (non-linear least squares) is now completed by a two-stage procedure, where the fas price is instrumented by tax duties and its own lag - see section 4.3 and appendix B.4 in the paper, and section 2.1.2 of this letter.

\item Based on your main comment 1, the paper has been rewritten so as to be more in line with Hummel's (2004) methodology. Specifically, we now start from the elasticity of total transport costs to the unit price $\beta$, which we show also corresponds to the share of additive costs. From this, we can deduce the additive / ad-valorem components ($t,\tau$) rather than the other way round (as in the submitted version). We thank the referee for pointing this out, as this contributes to a more straightforward and intuitive understanding of our estimation method.

### 2021-09-22 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Chanement partie modèle
 alléger main text

As in \cite{sorensen2014}, we adopt the two-country model of \cite{melitz} with monopolistic competition and endogenous firm entry.\footnote{\cite{Irrazabal_2015} adopt the multi-country model of \cite{chaney2008}, consistently with their database that documents the exports of Norwegian firms in various destination markets worldwide. We rather choose to retain the \cite{melitz} model, in its simplest form with one sector and two symmetric countries, picking up the average estimated values of transport costs based on our unique importer country, e.g. the US. Sticking to this canonical set-up allows us to illustrate the role of additive costs in a transparent and intuitive way.} As widely standard in the literature, we focus on steady-state analysis, running comparative statics analysis following a trade cost reduction. Since our focus in on the role of additive versus ad-valorem transport costs, we directly present the two-country version of the model, with the two countries (Home and Foreign) being perfectly symmetric.

@@

In each country, the representative household exogenously supplies $L$ units of labour and maximizes utility $\mathcal{U} = \left[ \int_{\omega \in \Omega}c(\omega)^{\frac{\sigma-1}{\sigma}} d\omega \right]^{\frac{\sigma}{\sigma-1}}$, with $\sigma>1$ the elasticity of substitution between varieties $\omega$. She chooses her consumption $c(\omega)$  within the set $\Omega$ of available varieties (made of both domestic and foreign varieties, endogenously defined), subject to her budget constraint: $\int_{\omega \in \Omega} p(\omega) c(\omega) dw \leq E$, with $p(\omega)$ the consumer price of variety $\omega$ and $E$ nominal expenditures. As standard, the optimal demand function for variety $\omega$ is:
\begin{eqnarray*}
c(\omega) &=& \left(\frac{p(\omega)}{P}  \right)^{-\sigma} \frac{E}{P}\\
\end{eqnarray*}
\noindent with the associated optimal price index $P$ equal to:
\begin{equation}
P = \left[ \int_{\omega \in \Omega}p(\omega)^{1-\sigma}d\omega\right]^{\frac{1}{1-\sigma}} \label{eq:CPI}
\end{equation}

@@

\paragraph{Profit-maximizing behaviors} Once entered, and conditional on being able to export, a firm adopts a pricing-to-market behavior by setting a specific price on each destination market.

On the domestic market, the objective is to maximize profit $\pi_d(\omega)= \left(p^d(\varphi) -\frac{1}{\varphi}  \right)c(\varphi)$, taken into account the consumer demand function $c(\varphi) = \left(\frac{p(\varphi)}{P}  \right)^{-\sigma} \frac{E}{P}$\footnote{In a monopolistic set-up, each firm (of productivity $\varphi$) is the sole producer of variety $\omega$, implying a one-to-one link between $\omega$ and $\varphi$, such that we could write $\omega(\varphi)$. For sake of notational simplicity, we omit this link and simply write the consumer demand function as a function of $\varphi$ directly.}
The optimal pricing behavior yields:
$$p^d(\varphi) = \frac{\sigma}{\sigma-1}\frac{1}{\varphi}$$
With a CES specification on household's preferences, the firm sets its price as a constant mark-up on marginal cost, which is inversely related to its productivity as for the domestic market. \medskip

Similarly as for the Home market, the firm sets a constant markup on its marginal cost, which is still a decreasing function of the firm's productivity $\varphi$, but also takes into account both components of trade costs.

Under the assumption of symmetric countries (i.e, implying $E=E^\ast$ and $P=P^\ast$), one can deduce the profits on the domestic and export markets ($\pi_d(\varphi)$ and $\pi_x(\varphi)$) respectively as:
\begin{eqnarray}
\pi_d(\varphi)  &=& \frac{r_d(\varphi)}{\sigma} - f = B \varphi^{\sigma-1} - f \label{eq:pid_rd}\\
\pi_x(\varphi) &=& \frac{r_x(\varphi)}{\sigma} - f_x = B \left[ \frac{\tau}{\varphi} + t\right]^{-(\sigma-1)} - f_x \label{eq:pix_rx}
\end{eqnarray}
\noindent with $B \equiv \frac{1}{\sigma-1}\left(\frac{\sigma}{\sigma-1}\right)^{-\sigma}P^{\sigma-1}E$ and where $r_d(\varphi)$ and $r_x(\varphi)$ denote the sales revenues on each market. Profits increase with productivity $\varphi$, and only sufficiently productive firms are able to cover the fixed costs of operating in a given market. Further, in presence of trade costs, a given firm of productivity $\varphi$ makes a lower export profit than on its domestic market, conditional on being productive enough to export. This drives us to determine the productivity threshold associated to the entry conditions.

\paragraph{Zero-cutoff profit conditions} Given the fixed costs on both the domestic and the export markets, only firms with a productivity above $\varphi^\ast$ will serve the domestic market, and those with $\varphi>\varphi_x^\ast$ will export abroad. With $\frac{\pi_d(\varphi^\ast)}{\delta}$ and  $\frac{\pi_x(\varphi_x^\ast)}{\delta}$ the expected profit on the domestic and export market respectively, the zero cut-off (ZCP) productivity levels for successful entry on each market should verify:
\begin{eqnarray*}
\frac{\pi_d(\varphi^\ast)}{\delta} = 0 &\Leftrightarrow & \varphi^\ast = \frac{1}{f^{\frac{1}{1-\sigma}}B^{\frac{-1}{1-\sigma}}}\\
\frac{\pi_x(\varphi_x^\ast)}{\delta} = 0 &\Leftrightarrow & \varphi_x^\ast = \frac{\tau}{f_x^{\frac{1}{1-\sigma}}B^{\frac{-1}{1-\sigma}} -t}
\end{eqnarray*}
The two productivity thresholds can be linked according to:
\begin{equation}
\frac{\varphi_x^\ast}{\tau+t\varphi_x^\ast} = \varphi^\ast \left( \frac{f}{f_x} \right)^{\frac{1}{1-\sigma}} \label{eq:link_thresholds}
\end{equation}

Following \cite{melitz} and the subsequent literature, we ensure selection on the export market, i.e. such that $\varphi_x^\ast > \varphi^\ast$. Making use of Equation (\ref{eq:link_thresholds}), this condition writes down as $\left[\tau+ t\varphi^\ast_x \right] \left( \frac{f}{f_x} \right)^{\frac{1}{1-\sigma}} >1$. Two comments can be made at this point. First, additive costs ($t>0$) make the selection condition more likely to happen everything else equal for any given values of ad-valorem and fixed costs. Put differently, additive costs somehow relax the constraint of the fixed cost of exporting. Second, due to additive costs ($t>0$), the export selection condition depends on the general equilibrium of the model (through $\varphi^\ast_x $) and cannot be imposed ex-ante by an appropriate restriction on the space parameter. We check this condition holds numerically in solving the model.\footnote{This is no longer the case under ad-valorem costs only. In this case, with $t=0$, we find the usual condition that $\varphi^\ast_x >\varphi^\ast$ iif $\tau^{\sigma-1}\frac{f_x}{f}>1$.}

@@

\paragraph{Aggregation} The general equilibrium is characterized by a mass $M$ of producing firms in each country associated with a distribution $\mu(\varphi)$ of productivity levels of a subset of $\left(0,\infty\right)$. Given the productivity threshold $\varphi^\ast$, $\mu(\varphi)$ is equal to the conditional distribution of $g(\varphi)$ on the subset $\left[\varphi^\ast, \infty\right)$:
\begin{eqnarray}
\mu(\varphi) &=& \left\{
\begin{array}{ll}
\frac{g(\varphi)}{1-G(\varphi^\ast)}, & \text{if } \varphi\geq \varphi^\ast  \\
0 & \text{otherwise}
\end{array}
\right.  \label{eq:muofphi}
\end{eqnarray}
\noindent with $1-G(\varphi^\ast)$ the probability of successful entry on the domestic market. Conditional on being active on the domestic market, a subset mass $M_x$ of firms export abroad. $\mu_x(\varphi)$ can be similarly defined as the conditional distribution of productivity on the export market, e.g. on the support $\left[ \varphi^\ast_x,\infty\right)$.

\noindent with $\widetilde{\varphi}(\varphi^\ast)$ and $\widetilde{\varphi}_x(\varphi_x^\ast)$ the weighted average of productivities of domestic and imported varieties respectively (defined in Appendix \ref{app:theoretical_model}). With $\widetilde{\varphi}_T \equiv \left[\frac{1}{M_T}\left(M\widetilde{\varphi}^{\sigma-1} + M_x \left( \frac{\widetilde{\varphi}_x}{\tau} \right)^{\sigma-1} \right)  \right]^{\frac{1}{1-\sigma}}$ the weighted average of firm productivities on the domestic market (including both local producers and foreign producers exporting at Home), the price index can be expressed as $P = M_T^{\frac{1}{1-\sigma}}\frac{1}{\rho \widetilde{\varphi}_T }$. As in \cite{melitz}, given our assumptions of wage normalization and a one-sector economy, welfare per worker is simply equal the inverse of the price level: $\mathcal{W} = \frac{w}{P}= P^{-1}$, leading to:

\begin{equation}
\mathcal{W} = \rho \widetilde{\varphi}_T M_T^{\frac{1}{\sigma-1}}\label{eq:Welfare}
\end{equation}

@@

Defining $\bar{\pi}$ as the average profit conditional to entry, this free-entry condition rewrites as:
\begin{equation}
\left(1-G(\varphi^\ast)\right)\frac{\bar{\pi}}{\delta} = f_e \label{eq:FEC}
\end{equation}

\noindent with $\left(1-G(\varphi^\ast)\right)$ the probability of successful entry. $\bar{\pi}$ can be expressed as $\bar{\pi} =\pi_d(\widetilde{\varphi}(\varphi^\ast)) + \rho_x \pi_x(\widetilde{\varphi}_x(\varphi_x^\ast))$, with $\pi_d(\widetilde{\varphi}(\varphi^\ast)) \equiv \bar{\pi}_d$ the average expected profit on the domestic market, $\pi_x(\widetilde{\varphi}_x(\varphi_x^\ast))\equiv \bar{pi}_x$ the average expected export profit and $\rho_x$ the probability of exporting (conditional on entry on the domestic market), equal to $\rho_x = \frac{1-G(\varphi_x^\ast)}{1-G(\varphi^\ast)}$.

Making use of the above elements, we finally get the zero-cut off profit condition in the open economy with additive costs as:
\begin{equation}
\bar{\pi} = \left\{\left(\frac{\widetilde{\varphi}^\ast}{\varphi^\ast}\right)^{\sigma-1}-1 \right\}f +  \frac{1-G(\varphi_x^\ast)}{1-G(\varphi^\ast)}\left\{\left[\left(\frac{\widetilde{\varphi}_x^\ast}{\varphi_x^\ast}\right)\left(\frac{\tau+ t \varphi^\ast_x}{\tau+ t \widetilde{\varphi}^\ast_x}\right)\right]^{\sigma-1}-1 \right\}f_x \label{eq:ZCP}
\end{equation}
\noindent with $\widetilde{\varphi}^\ast$ and $\widetilde{\varphi}_x^\ast$ given by Equations (\ref{eq:def_phitilde}) and (\ref{eq:def_phitildex}).

\paragraph{Summary} Equations (\ref{eq:def_phitilde}), (\ref{eq:def_phitildex}), (\ref{eq:ZCP}), (\ref{eq:link_thresholds}) and (\ref{eq:FEC}) determine a system of interdependent equations in five endogenous variables $\left\{\bar{\pi}, \widetilde{\varphi}, \widetilde{\varphi}_x, \varphi^\ast, \varphi^\ast_x \right\}$. From this, we can deduce the equilibrium values of the remaining set of variables (as detailed in Appendix \ref{app:theoretical_model}).

@@

As standard in this literature (\cite{Irrazabal_2015}, \cite{melitz-redding-Handbk-IT-2014}), the heterogenity in firm productivity is assumed to be given by a Pareto distribution. As shown in \cite{melitz-redding-Handbk-IT-2014}, the Pareto distribution indeed allows for a full analytical solving of the M\'{e}litz model. This is no longer the case in the presence of additive costs (see Appendix \ref{app:theoretical_model}). In this case, we need to rely on the model's simulations to determine the steady state. This drives us to calibrate the structural parameters of the model. To do so, we dwell on values commonly retained in the literature, as reported in Table \ref{tab:calib_horsTC}. The one exception is the value for the two additive and ad-valorem transport costs, for which we use our empirical estimates of Section \ref{sec:results_decomposition}.

\begin{table}[htbp]
  \centering
  \caption{Calibration (1)} \label{tab:calib_horsTC}
\begin{center}
	\input{donnees_calibration.tex}
\end{center}
{\parbox[l]{13cm}{ \vspace{4pt}\footnotesize{Notes: $f_x$ can take two values, depending on the share of exporters considered that might differ between the initial steady state (21\%, based on early 1980s' value) and the final steady state (39\%, based on 2000's value.), according to the references provided above. BEJK (2003) refers to \cite{BEJK-AER-03}.}}}
\end{table}

Following \cite{ghironi}, $f$ such that all firms produce in autarky (i.e., such that $\varphi^{\ast,a} = \varphi_{\text{min}}$. The calibration of the fixed export cost obeys the following logic. As in \cite{ghironi}, $f_x$ is endogenously revealed to match a given share of exporting firms at the steady state. Further, \cite{Lincoln_McCallum2018} document the large increase in the number of exporting firms in the US between the mid 1980s et the mid 2000s, with a share of exporting firms raising by 52\% over this period. Accordingly, we will assess the effects of the trade liberalization assuming a joined reduction in both the variable transport costs ($\tau, t$, based on our empirical estimates) and the fixed export cost $f_x$. Specifically, we endogenously determine the initial value of $f_x$ such that the initial steady state (with 1974 values of transport costs) implies a share of exporting firms equal to 21\%, as in  \cite{ghironi} based on the value estimated by \cite{BEJK-AER-03} in the early 1990s. In the final steady state, $f_x$ will be revealed such that this share of exporting plants has increased by 85\% (i.e., from 21\% to 39\%), based on the evidence reported in \cite{Lincoln_McCallum2018}.\smallskip

The calibration of transport costs parameters relies on our empirical estimates. We notably illustrate the consequences of trade liberalization by comparing the equilibrium based on the 1974 values of transport costs (at the beginning of our sample), versus those of 2019 (at the very end of our estimation period), in both cases on only ad-valorem transport costs and in the presence of both additive and ad-valorem costs. Calibration of transport costs is displayed in Table \ref{tab:calib_TC}.

@@

@@

@@

Following \cite{melitz}, and decomposing the set of available varieties into $\Omega_d$, $\Omega_x$ the set of varieties respectively produced at Home and imported, one can rewrite the price index (\ref{eq:CPI}) as:
\begin{eqnarray*}
P &=& \left[\int_{\omega \in \Omega_d} p_d^{1-\sigma}(\omega)d\omega + \int_{\omega \in \Omega_x} p_x^{1-\sigma}(\omega)d\omega  \right]^{\frac{1}{1-\sigma}} \\
&=& \left[\int_{0}^\infty p_d^{1-\sigma}(\varphi)M\mu(\varphi)d\varphi + \int_{0}^\infty p_x^{1-\sigma}(\varphi)M_x \mu_x(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}}
\end{eqnarray*}
Making use of Equation (\ref{eq:muofphi}), the price index reads as:
\begin{eqnarray*}
P &=& \left[\frac{M}{1-G(\varphi^\ast)}\int_{\varphi^\ast}^\infty p_d^{1-\sigma}(\varphi)g(\varphi)d\varphi + \frac{M_x}{1-G(\varphi_x^\ast)}\int_{\varphi^\ast_x}^\infty p_x^{1-\sigma}(\varphi)g(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}} \\
\text{with}&& \left\{
\begin{array}{lll}
p_d(\varphi)&=& \frac{\sigma}{\sigma-1} \frac{1}{\varphi}\\
p_x(\varphi)&=& \frac{\sigma}{\sigma-1} \left[\frac{\tau}{\varphi} +t\right]
\end{array}
\right.
\end{eqnarray*}
Accordingly, the price index can be rewritten as:
$$P = \left(\frac{\sigma}{\sigma-1}\right)\left[\frac{M}{1-G(\varphi^\ast)}\int_{\phi^\ast}^\infty \phi^{\sigma-1}g(\varphi)d\varphi + \frac{M_x}{1-G(\varphi_x^\ast)}\int_{\varphi^\ast_x}^\infty \left[\varphi \left(\frac{\tau}{\tau+t \varphi}  \right)  \right]^{\sigma-1}g(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}}$$

@@

>>>>

We rely on the model developed by \cite{sorensen2014}, which amends the two-country model of \cite{melitz} with monopolistic competition and endogenous firm entry to include additive costs.\footnote{\cite{Irrazabal_2015} adopt the multi-country model of \cite{chaney2008}, consistently with their database that documents the exports of Norwegian firms in various destination markets worldwide. We rather choose to retain the \cite{melitz} model, in its simplest form with one sector and two symmetric countries, picking up the average estimated values of transport costs based on our unique importer country, e.g. the US. Sticking to this canonical set-up allows us to illustrate the role of additive costs in a transparent and intuitive way.} Since our focus in on the role of additive versus ad-valorem transport costs, we directly present the two-country version of the model, with the two countries (Home and Foreign) being perfectly symmetric. For sake of space saving, we only present here the building blocks of the model. More details can be found in Appendix \ref{app:theoretical_model}.

@@

In each country, the representative household exogenously supplies $L$ units of labour and maximizes utility $\mathcal{U} = \left[ \int_{\omega \in \Omega}c(\omega)^{\frac{\sigma-1}{\sigma}} d\omega \right]^{\frac{\sigma}{\sigma-1}}$, with $\sigma>1$ the elasticity of substitution between varieties $\omega$. She chooses her consumption $c(\omega)$  within the set $\Omega$ of available varieties (made of both domestic and foreign varieties, endogenously defined), subject to her budget constraint: $\int_{\omega \in \Omega} p(\omega) c(\omega) dw \leq E$, with $p(\omega)$ the consumer price of variety $\omega$ and $E$ nominal expenditures. As standard, the optimal demand function for variety $\omega$ is: $c(\omega) = \left(\frac{p(\omega)}{P}  \right)^{-\sigma} \frac{E}{P}$ with the associated optimal price index $P$ equal to $P = \left[ \int_{\omega \in \Omega}p(\omega)^{1-\sigma}d\omega\right]^{\frac{1}{1-\sigma}} $.

@@

\paragraph{Profit-maximizing behaviors} Once entered, and conditional on being able to export, a firm adopts a pricing-to-market behavior by setting a specific price on each destination market. For each destination market, he firm sets a constant markup on its marginal cost, which is a decreasing function of the firm's productivity $\varphi$, but also takes into account both components of trade costs on the export market, according to:
\begin{eqnarray}
p_d(\varphi) &=& \frac{\sigma}{\sigma-1}\frac{1}{\varphi} \notag \\
p_x(\varphi) &=& \frac{\sigma}{\sigma-1}\left[\frac{\tau}{\varphi} +t \right] \label{eq:px}
\end{eqnarray}

Under the assumption of symmetric countries (i.e, implying $E=E^\ast$ and $P=P^\ast$), one can deduce the profits on the domestic and export markets ($\pi_d(\varphi)$ and $\pi_x(\varphi)$) respectively as:
\begin{eqnarray}
\pi_d(\varphi)  &=& \frac{r_d(\varphi)}{\sigma} - f = B \varphi^{\sigma-1} - f \label{eq:pid_rd}\\
\pi_x(\varphi) &=& \frac{r_x(\varphi)}{\sigma} - f_x = B \left[ \frac{\tau}{\varphi} + t\right]^{-(\sigma-1)} - f_x \label{eq:pix_rx}
\end{eqnarray}
\noindent with $B \equiv \frac{1}{\sigma-1}\left(\frac{\sigma}{\sigma-1}\right)^{-\sigma}P^{\sigma-1}E$ and where $r_d(\varphi)$ and $r_x(\varphi)$ denote the sales revenues on each market (see Appendix \ref{app:theoretical_model} for a detailed expression). Profits increase with productivity $\varphi$, and only sufficiently productive firms are able to cover the fixed costs of operating in a given market. Further, in presence of trade costs, a given firm of productivity $\varphi$ makes a lower export profit than on its domestic market, conditional on being productive enough to export. This drives us to determine the productivity threshold associated to the entry conditions.

\paragraph{Zero-cutoff profit conditions} Given the fixed costs on both the domestic and the export markets, only firms with a productivity above $\varphi^\ast$ will serve the domestic market, and those with $\varphi>\varphi_x^\ast$ will export abroad.  The two productivity thresholds can be linked according to:
\begin{equation}
\frac{\varphi_x^\ast}{\tau+t\varphi_x^\ast} = \varphi^\ast \left( \frac{f}{f_x} \right)^{\frac{1}{1-\sigma}} \label{eq:link_thresholds}
\end{equation}

Following \cite{melitz} and the subsequent literature, we ensure selection on the export market, i.e. such that $\varphi_x^\ast > \varphi^\ast$. Making use of Equation (\ref{eq:link_thresholds}), this condition writes down as $\left[\tau+ t\varphi^\ast_x \right] \left( \frac{f}{f_x} \right)^{\frac{1}{1-\sigma}} >1$. Due to additive costs ($t>0$), the export selection condition depends on the general equilibrium of the model (through $\varphi^\ast_x $) and cannot be imposed ex-ante by an appropriate restriction on the space parameter. We check this condition holds numerically in solving the model.\footnote{This is no longer the case under ad-valorem costs only. In this case, with $t=0$, we find the usual condition that $\varphi^\ast_x >\varphi^\ast$ iif $\tau^{\sigma-1}\frac{f_x}{f}>1$.}

@@

\paragraph{Aggregation} The general equilibrium is characterized by a mass $M$ of producing firms in each country associated with a distribution $\mu(\varphi)$ of productivity levels of a subset of $\left(0,\infty\right)$. Given the productivity threshold $\varphi^\ast$, $\mu(\varphi)$ is equal to the conditional distribution of $g(\varphi)$ on the subset $\left[\varphi^\ast, \infty\right)$:
\begin{eqnarray}
\mu(\varphi) &=& \left\{
\begin{array}{ll}
\frac{g(\varphi)}{1-G(\varphi^\ast)}, & \text{if } \varphi\geq \varphi^\ast  \\
0 & \text{otherwise}
\end{array}
\right.  \label{eq:muofphi}
\end{eqnarray}
\noindent with $1-G(\varphi^\ast)$ the probability of successful entry on the domestic market. Conditional on being active on the domestic market, a subset mass $M_x$ of firms export abroad. $\mu_x(\varphi)$ can be similarly defined as the conditional distribution of productivity on the export market, e.g. on the support $\left[ \varphi^\ast_x,\infty\right)$.
Further defining $M_T = M+M_x$ as the total number of varieties accessible to the consumers, $\widetilde{\varphi}_T$ the weighted average of firms productivities on the domestic market, one can show that the welfare per worker can be written as (see Appendix \ref{app:theoretical_model}): 
\begin{equation}
\mathcal{W} = \rho \widetilde{\varphi}_T M_T^{\frac{1}{\sigma-1}} \label{eq:Welfare}
\end{equation}

@@

Defining $\bar{\pi}$ as the average profit conditional to entry, this free-entry condition rewrites as:
\begin{equation}
\left(1-G(\varphi^\ast)\right)\frac{\bar{\pi}}{\delta} = f_e \label{eq:FEC}
\end{equation}
As shown in Appendix \ref{app:theoretical_model}, it can be rewritten as:
\begin{equation}
\bar{\pi} = \left\{\left(\frac{\widetilde{\varphi}^\ast}{\varphi^\ast}\right)^{\sigma-1}-1 \right\}f +  \frac{1-G(\varphi_x^\ast)}{1-G(\varphi^\ast)}\left\{\left[\left(\frac{\widetilde{\varphi}_x^\ast}{\varphi_x^\ast}\right)\left(\frac{\tau+ t \varphi^\ast_x}{\tau+ t \widetilde{\varphi}^\ast_x}\right)\right]^{\sigma-1}-1 \right\}f_x \label{eq:ZCP}
\end{equation}
\noindent with $\widetilde{\varphi}^\ast$ and $\widetilde{\varphi}_x^\ast$ the weighted average productivities of domestic and exporting firms respectively (see Equations (\ref{eq:def_phitilde}) and (\ref{eq:def_phitildex}) in Appendix \ref{app:theoretical_model}).

@@

As standard in this literature (\cite{Irrazabal_2015}, \cite{melitz-redding-Handbk-IT-2014}), the heterogenity in firm productivity is assumed to be given by a Pareto distribution. As shown in \cite{melitz-redding-Handbk-IT-2014}, the Pareto distribution indeed allows for a full analytical solving of the M\'{e}litz model. This is no longer the case in the presence of additive costs (see Appendix \ref{app:theoretical_model}). In this case, we need to rely on the model's simulations to determine the steady state. This drives us to calibrate the structural parameters of the model. To do so, we dwell on values commonly retained in the literature, as reported in Table \ref{tab:calib_horsTC}. The one exception is the value for the two additive and ad-valorem transport costs, for which we use our empirical estimates of Section \ref{sec:results_decomposition} for the years 1974 and 2019, as reported in Table \ref{tab:calib_TC}.

\begin{table}[htbp]
  \centering
  \caption{Calibration (1)} \label{tab:calib_horsTC}
\begin{center}
	\input{donnees_calibration.tex}
\end{center}
{\parbox[l]{13cm}{ \vspace{4pt}\footnotesize{Notes: $f$ endogenously revealed at the autarky case, such that all firms produce in autarky. $f_x$ can take two values, depending on the share of exporters considered that might differ between the initial steady state (21\%, based on early 1980s' value) and the final steady state (39\%, based on 2000's value.), according to the references provided above. BEJK (2003) refers to \cite{BEJK-AER-03}.}}}
\end{table}

@@

We notably illustrate the consequences of trade liberalization by comparing the equilibrium based on the 1974 values of transport costs (at the beginning of our sample), versus those of 2019 (at the very end of our estimation period), in both cases on only ad-valorem transport costs and in the presence of both additive and ad-valorem costs. Further, \cite{Lincoln_McCallum2018} document the large increase in the number of exporting firms in the US between the mid 1980s et the mid 2000s, with a share of exporting firms raising by 52\% over this period. This can be captured in the model through a reduction in the fixed export cost $f_x$. Accordingly, we will assess the effects of the trade liberalization assuming a joined reduction in both the variable transport costs ($\tau, t$, based on our empirical estimates) and the fixed export cost $f_x$.\footnote{We endogenously determine the initial value of $f_x$ such that the initial steady state (with 1974 values of transport costs) implies a share of exporting firms equal to 21\%, as in  \cite{ghironi} based on the value estimated by \cite{BEJK-AER-03} in the early 1990s. In the final steady state, $f_x$ will be revealed such that this share of exporting plants has increased by 85\% (i.e., from 21\% to 39\%), based on the evidence reported in \cite{Lincoln_McCallum2018}, along with the 2019 values of variable transport costs}

@@

\subsubsection{Firms}

\paragraph{Profit-maximizing behavior}

On the domestic market, the objective is to maximize profit $\pi_d(\omega)= \left(p^d(\varphi) -\frac{1}{\varphi}  \right)c(\varphi)$, taking into account the consumer demand function $c(\varphi) = \left(\frac{p(\varphi)}{P}  \right)^{-\sigma} \frac{E}{P}$. In a monopolistic set-up, each firm (of productivity $\varphi$) is the sole producer of variety $\omega$, implying a one-to-one link between $\omega$ and $\varphi$, such that we could write $\omega(\varphi)$. For sake of notational simplicity, we omit this link and simply write the consumer demand function as a function of $\varphi$ directly. 
The optimal pricing behavior yields:
$$p^d(\varphi) = \frac{\sigma}{\sigma-1}\frac{1}{\varphi}$$
With a CES specification on household's preferences, the firm sets its price as a constant mark-up on marginal cost, which is inversely related to its productivity as for the domestic market. \medskip

\paragraph{Zero-cutoff profit conditions} With $\frac{\pi_d(\varphi^\ast)}{\delta}$ and  $\frac{\pi_x(\varphi_x^\ast)}{\delta}$ the expected profit on the domestic and export market respectively, the zero cut-off (ZCP) productivity levels for successful entry on each market should verify:
\begin{eqnarray*}
\frac{\pi_d(\varphi^\ast)}{\delta} = 0 &\Leftrightarrow & \varphi^\ast = \frac{1}{f^{\frac{1}{1-\sigma}}B^{\frac{-1}{1-\sigma}}}\\
\frac{\pi_x(\varphi_x^\ast)}{\delta} = 0 &\Leftrightarrow & \varphi_x^\ast = \frac{\tau}{f_x^{\frac{1}{1-\sigma}}B^{\frac{-1}{1-\sigma}} -t}
\end{eqnarray*}

@@

Following \cite{melitz}, and decomposing the set of available varieties into $\Omega_d$, $\Omega_x$ the set of varieties respectively produced at Home and imported, one can rewrite the price index as:
\begin{eqnarray*}
P &=& \left[\int_{\omega \in \Omega_d} p_d^{1-\sigma}(\omega)d\omega + \int_{\omega \in \Omega_x} p_x^{1-\sigma}(\omega)d\omega  \right]^{\frac{1}{1-\sigma}} \\
&=& \left[\int_{0}^\infty p_d^{1-\sigma}(\varphi)M\mu(\varphi)d\varphi + \int_{0}^\infty p_x^{1-\sigma}(\varphi)M_x \mu_x(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}}
\end{eqnarray*}
Making use of Equation (\ref{eq:muofphi}), the price index reads as:
\begin{eqnarray*}
P &=& \left[\frac{M}{1-G(\varphi^\ast)}\int_{\varphi^\ast}^\infty p_d^{1-\sigma}(\varphi)g(\varphi)d\varphi + \frac{M_x}{1-G(\varphi_x^\ast)}\int_{\varphi^\ast_x}^\infty p_x^{1-\sigma}(\varphi)g(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}} \\
\text{with}&& \left\{
\begin{array}{lll}
p_d(\varphi)&=& \frac{\sigma}{\sigma-1} \frac{1}{\varphi}\\
p_x(\varphi)&=& \frac{\sigma}{\sigma-1} \left[\frac{\tau}{\varphi} +t\right]
\end{array}
\right.
\end{eqnarray*}
Accordingly, the price index can be rewritten as:
$$P = \left(\frac{\sigma}{\sigma-1}\right)\left[\frac{M}{1-G(\varphi^\ast)}\int_{\phi^\ast}^\infty \phi^{\sigma-1}g(\varphi)d\varphi + \frac{M_x}{1-G(\varphi_x^\ast)}\int_{\varphi^\ast_x}^\infty \left[\varphi \left(\frac{\tau}{\tau+t \varphi}  \right)  \right]^{\sigma-1}g(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}}$$

@@

\noindent with $\widetilde{\varphi}(\varphi^\ast)$ and $\widetilde{\varphi}_x(\varphi_x^\ast)$ the weighted average of productivities of domestic and imported varieties respectively defined in Equations (\ref{eq:def_phitilde}) and (\ref{eq:def_phitildex}). With $\widetilde{\varphi}_T \equiv \left[\frac{1}{M_T}\left(M\widetilde{\varphi}^{\sigma-1} + M_x \left( \frac{\widetilde{\varphi}_x}{\tau} \right)^{\sigma-1} \right)  \right]^{\frac{1}{1-\sigma}}$ the weighted average of firm productivities on the domestic market (including both local producers and foreign producers exporting at Home), the price index can be expressed as $P = M_T^{\frac{1}{1-\sigma}}\frac{1}{\rho \widetilde{\varphi}_T }$. As in \cite{melitz}, given our assumptions of wage normalization and a one-sector economy, welfare per worker is simply equal the inverse of the price level: $\mathcal{W} = \frac{w}{P}= P^{-1}$, leading to:
